BumpyMatrix: a Bioconductor package to represent a 2-dimensional array of non-scalar objects

### 2023-01-18 paper.Rmd
Minor rewording here and there.

Let's mock up some data for a multiplexed FISH experiment.
This consists of a `DataFrame` (Bioconductor's wrapper around the base `data.frame` class) where each row contains the coordinates of a single detected transcript molecule in a particular cell.

@@

We use the `splitAsBumpyMatrix()` function to create a `BumpyDataFrameMatrix` where the rows are genes and the columns are cells.
Each entry of this `BumpyDataFrameMatrix` is itself a `DataFrame` that corresponds to a particular gene/cell combination,
and containing the x/y-coordinates for all transcript molecules of that gene in that cell.
Each `DataFrame` may have zero, one or multiple rows, depending on the cell's expression of the gene.

@@

We can now treat `mat` in the same manner as any other matrix-like R object.
For example, we can slice by row and column, equivalent to filtering our original `df` by gene or cell respectively.

@@

# Computing the Euclidean distance of each transcript from the centroid.
# Transpositions are necessary to ensure that the cell centroid coordinates
# are recycled along the cells, not along the features.
squared_x <- (t(mat[,,"x"]) - x_cell)^2 
squared_y <- (t(mat[,,"y"]) - y_cell)^2
dist <- t(sqrt(squared_x + squared_y))
dist
```

@@

>>>>

To demonstrate the use of the `BumpyMatrix` class, let's mock up some data for a multiplexed RNA fluorescence _in situ_ hybridization (RNA-FISH) experiment.
Our data consists of a `DataFrame` (Bioconductor's wrapper around the base `data.frame` class) where each row contains the coordinates of a single detected transcript molecule.
We assume that demultiplexing and cell segmentation have already been performed, such that each detected molecule is also annotated with its gene identity and its cell of origin.

@@

We use the `splitAsBumpyMatrix()` function to create a `BumpyDataFrameMatrix`, a 2-dimensional matrix abstraction where the rows are genes and the columns are cells.
Each entry of this `BumpyDataFrameMatrix` is itself a `DataFrame` that corresponds to a particular gene/cell combination and contains the x/y-coordinates for all transcript molecules of that gene in that cell.
Each `DataFrame` may have zero, one or multiple rows, depending on the cell's expression of the gene.

@@

We can now manipulate `mat` in the same manner as any other matrix-like R object.
For example, we can slice by row and column, equivalent to filtering our original `df` by gene or cell respectively.

@@

# Computing the Euclidean distance of each transcript from the centroid.
# Transpositions ensure that the cell centroid coordinates are recycled along
# the cells, not along the features.
squared_x <- (t(mat[,,"x"]) - x_cell)^2 
squared_y <- (t(mat[,,"y"]) - y_cell)^2
dist <- t(sqrt(squared_x + squared_y))
dist
```

@@

# Examples of other applications
